---
title: "Analysis_presentation"
author: "Lisa Lemmens"
date: "2019 M07 22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#loading necessary packages (I do not know whether they are all necessary :-)) 
```{r}

library(reshape2)
library(lme4)
library(ggplot2)
library(dplyr)
library(tidyr)
library("ggpubr")
library(readr)
```

#Reading the data (very sloppy way of reading the data)
```{r}
exp_001 <-read.csv("data/exp_001.csv")
exp_001 <- mutate(exp_001,id =001)
exp_003 <-read.csv("data/exp_003.csv")
exp_003 <- mutate(exp_003,id =003)
exp_004 <-read.csv("data/exp_004.csv")
exp_004 <- mutate(exp_004,id =004)
exp_005 <-read.csv("data/exp_005.csv")
exp_005 <- mutate(exp_005,id =005)
exp_006 <-read.csv("data/exp_006.csv")
exp_006 <- mutate(exp_006,id =006)
exp_007 <-read.csv("data/exp_007.csv")
exp_007 <- mutate(exp_007,id =007)
exp_008 <-read.csv("data/exp_008.csv")
exp_008 <- mutate(exp_008,id =008)
exp_009 <-read.csv("data/exp_009.csv")
exp_009 <- mutate(exp_009,id =009)
exp_010 <-read.csv("data/exp_010.csv")
exp_010 <- mutate(exp_010,id =010)
exp_011 <-read.csv("data/exp_011.csv")
exp_011 <- mutate(exp_011,id =011)
exp_012 <-read.csv("data/exp_012.csv")
exp_012 <- mutate(exp_012,id =012)
exp_013 <-read.csv("data/exp_013.csv")
exp_013 <- mutate(exp_013,id =013)
exp_014 <-read.csv("data/exp_014.csv")
exp_014 <- mutate(exp_014,id =014)
exp_015 <-read.csv("data/exp_015.csv")
exp_015 <- mutate(exp_015,id =015)
exp_016 <-read.csv("data/exp_016.csv")
exp_016 <- mutate(exp_016,id =016)
exp_017 <-read.csv("data/exp_017.csv")
exp_017 <- mutate(exp_017,id =017)
exp_018 <-read.csv("data/exp_018.csv")
exp_018 <- mutate(exp_018,id =018)
exp_019 <-read.csv("data/exp_019.csv")
exp_019 <- mutate(exp_019,id =019)
exp_020 <-read.csv("data/exp_020.csv")
exp_020 <- mutate(exp_020,id =020)
exp_021 <-read.csv("data/exp_021.csv")
exp_021 <- mutate(exp_021,id =021)
exp_022 <-read.csv("data/exp_022.csv")
exp_022 <- mutate(exp_022,id =022)
exp_023 <-read.csv("data/exp_023.csv")
exp_023 <- mutate(exp_023,id =023)
exp_024 <-read.csv("data/exp_024.csv")
exp_024 <- mutate(exp_024,id =024)
exp_025 <-read.csv("data/exp_025.csv")
exp_025 <- mutate(exp_025,id =025)

exp_301 <-read.csv("data/exp_301.csv")
exp_301<-mutate(exp_301,id=301)
exp_302 <-read.csv("data/exp_302.csv")
exp_302<-mutate(exp_302,id=302)
exp_303 <-read.csv("data/exp_303.csv")
exp_303<-mutate(exp_303,id=303)
exp_305 <-read.csv("data/exp_305.csv")
exp_305<-mutate(exp_305,id=305)
exp_306 <-read.csv("data/exp_306.csv")
exp_306<-mutate(exp_306,id=306)
exp_307 <-read.csv("data/exp_307.csv")
exp_307<-mutate(exp_307,id=307)
exp_308 <-read.csv("data/exp_308.csv")
exp_308<-mutate(exp_308,id=308)
exp_309 <-read.csv("data/exp_309.csv")
exp_309<-mutate(exp_309,id=309)
exp_310 <-read.csv("data/exp_310.csv")
exp_310<-mutate(exp_310,id=310)
exp_311 <-read.csv("data/exp_311.csv")
exp_311<-mutate(exp_311,id=311)
exp_312 <-read.csv("data/exp_312.csv")
exp_312<-mutate(exp_312,id=312)
exp_313 <-read.csv("data/exp_313.csv")
exp_313<-mutate(exp_313,id=313)
exp_314 <-read.csv("data/exp_314.csv")
exp_314<-mutate(exp_314,id=314)
exp_317 <-read.csv("data/exp_317.csv")
exp_317<-mutate(exp_317,id=317)
exp_318 <-read.csv("data/exp_318.csv")
exp_318<-mutate(exp_318,id=318)
exp_319 <-read.csv("data/exp_319.csv")
exp_319<-mutate(exp_319,id=319)
exp_320 <-read.csv("data/exp_320.csv")
exp_320<-mutate(exp_320,id=320)
exp_323 <-read.csv("data/exp_323.csv")
exp_323<-mutate(exp_323,id=323)
exp_324 <-read.csv("data/exp_324.csv")
exp_324<-mutate(exp_324,id=324)
exp_325 <-read.csv("data/exp_325.csv")
exp_325<-mutate(exp_325,id=325)
exp_326 <-read.csv("data/exp_326.csv")
exp_326<-mutate(exp_326,id=326)
exp_327 <-read.csv("data/exp_327.csv")
exp_327<-mutate(exp_327,id=327)
exp_328 <-read.csv("data/exp_328.csv")
exp_328<-mutate(exp_328,id=328)
exp_329 <-read.csv("data/exp_329.csv")
exp_329<-mutate(exp_329,id=329)
exp_330 <-read.csv("data/exp_330.csv")
exp_330<-mutate(exp_330,id=330)
df<-bind_rows(exp_001,exp_003,exp_004,exp_005,exp_006,exp_007,exp_008,exp_009, exp_010,exp_011,exp_012,exp_013, exp_014,exp_015,exp_016,exp_017,exp_018,exp_019,exp_020,exp_021,exp_022,exp_023,exp_024,exp_025,exp_301, exp_302,exp_303, exp_305, exp_306, exp_307, exp_308, exp_309, exp_310, exp_311, exp_312, exp_313, exp_314, exp_317, exp_318, exp_319, exp_320, exp_323, exp_324, exp_325, exp_326, exp_327, exp_328, exp_329, exp_330)

#Create factor variable for two groups
df$group[df$id < 100] <- "ASD" 
df$group[df$id > 100]<- "TD"
df$group=factor(df$group)
df$trial_sigma = factor(df$trial_sigma)
df$id = factor(df$id)

df <- df %>% mutate(final = ifelse(final_ori > 180, final_ori - 360, final_ori)) #variable final, goes from -180 to +180, in line with presented orientations ( -28° to 118°) instead of final_ori that goes from 0 to 360 degrees 

```

#create factor variables for means of priors
```{r}
# prior_mean is factor variable for mean of prior
df$prior_mean[df$block_mu == 22] <- "22" 
df$prior_mean[df$block_mu == 68] <- "68"

# Session variable indicates whether the first prior was the one with 22 mean or 68 mean.
df$session[df$block_mu == 22 & df$ block_index == 0] <- "22_first" 
df$session[df$block_mu == 22 & df$ block_index == 1] <- "22_first"
df$session[df$block_mu == 22 & df$ block_index == 2] <- "22_first"
df$session[df$block_mu == 22 & df$ block_index == 3] <- "22_first"
df$session[df$block_mu == 22 & df$ block_index == 4] <- "22_first"
df$session[df$block_mu == 22 & df$ block_index == 5] <- "22_first"
df$session[df$block_mu == 68 & df$ block_index == 6] <- "22_first"
df$session[df$block_mu == 68 & df$ block_index == 7] <- "22_first"

df$session[df$block_mu == 68 & df$ block_index == 0] <- "68_first"
df$session[df$block_mu == 68 & df$ block_index == 1] <- "68_first"
df$session[df$block_mu == 68 & df$ block_index == 2] <- "68_first"
df$session[df$block_mu == 68 & df$ block_index == 3] <- "68_first"
df$session[df$block_mu == 68 & df$ block_index == 4] <- "68_first"
df$session[df$block_mu == 68 & df$ block_index == 5] <- "68_first"
df$session[df$block_mu == 22 & df$ block_index == 6] <- "68_first"
df$session[df$block_mu == 22 & df$ block_index == 7] <- "68_first"

#Create factor variable for blocks of 100 trials
df$tr_100[df$block_index < 2] <- "1" #tr_100 gives blocks of 100 trials
df$tr_100[df$block_index > 1 & df$block_index < 4] <- "2"
df$tr_100[df$block_index > 3 & df$block_index < 6] <- "3"
df$tr_100[df$block_index > 5] <- "4"

#Create factor variable to indicate whether it is the first or the second prior
df$prior[df$block_index < 6] <- "prior 1" #prior 1 or prior 2
df$prior[df$block_index > 5] <- "prior 2"

```
#Delete practice trials
```{r}
df <- df %>% 
  filter(block_index > -1) %>% #delete practice trials
  mutate(distance_prior_response = final - block_mu,distance_prior = trial_mu - block_mu) %>% #distance_prior_response is the final chosen direction minus mean  of the prior in that block; distance_prior is the presented motion direction minu the mean of the prior in that block. 
  mutate(distance_prior_response = ifelse(distance_prior_response > 180, distance_prior_response - 360, distance_prior_response))%>%
  mutate(distance_prior_response = ifelse(distance_prior_response < -180, distance_prior_response + 360, distance_prior_response))%>%
  mutate(bias=distance_prior_response - distance_prior)%>%
  mutate(bias = ifelse(bias < -180, bias + 360, bias)) %>%
  mutate(bias = ifelse(bias > 180, bias - 360, bias)) %>%
  mutate(slope=(distance_prior_response)/(trial_mu - block_mu)) %>%#slope like in Vilares (see supplementary)
  mutate(arc_slope =(atan(-0.5 +slope)/pi)+0.5)  %>% #Instantaneous slope like in Vilares (see supplementary)
  mutate(rt_norm=rt/(abs(final_ori-initial_ori)))%>% #rt normalised by distance between chosen orientation and initial orientation of the presented fishing rod
  mutate(distance_prior_response_conv = ifelse(session =="22_first", distance_prior_response*(-1), distance_prior_response))%>% #Convert the responses of sessions with 22 degree prior first into 68 degrees first by inverting the sign.
  mutate(distance_prior_conv = ifelse(session =="22_first", distance_prior*(-1), distance_prior))%>% #same for the distance of the presented directions from the priors in the 22° first sessions.
  mutate(bias_conv = ifelse(session =="22_first", bias*(-1), bias)) #same for bias.

#Check distributions of variables 
df$block_index=factor(df$block_index)
ggplot(df, aes(distance_prior_response)) + geom_histogram(binwidth = 5)
ggplot(df, aes(final)) + geom_histogram(binwidth = 10) + facet_grid(~prior_mean) + geom_vline(xintercept=22, color='blue') + geom_vline(xintercept=68,color='red')


ggplot(df, aes(bias_conv)) + geom_histogram(binwidth = 5) 
ggplot(df, aes(trial_mu)) + geom_histogram(binwidth = 10) 
ggplot(df, aes(final)) + geom_histogram(binwidth = 10) 

```

#outliers?
#root mean square error and mean absolute distance
```{r}


error <- df %>%
  group_by(id, group, trial_sigma) %>%
  summarize(rms_error = sqrt(mean(distance_prior_response^2)), abs_error = mean(abs(distance_prior_response))) 
#calculate rms error and absolute error over the whole task for each individual per condition of trial_sigma

error

#Figures
ggboxplot(error, x = "trial_sigma", y = "rms_error", add= "jitter",color = "group",legend = "right", ylab="Root mean square error", xlab = "Variability" )  + scale_color_manual(values=c("darkorange", "darkslategrey"))

ggboxplot(error, x = "trial_sigma", y = "abs_error", color = "group", add= "jitter" ,legend = "right", ylab="Absolute error", xlab = "Variability" )+ scale_color_manual(values=c("darkorange", "darkslategrey"))


error<-df%>%
  group_by(id,trial_sigma, group, tr_100)%>%
  summarize(rms_error = sqrt(mean(distance_prior_response^2)), abs_error = mean(abs(distance_prior_response)))

#Summarytable of rms error and abslute error per group.
error %>%group_by(id,trial_sigma, group)%>%
      summarize(n = n(),rms_error = mean(rms_error), abs_error = mean(abs_error))%>%
      group_by(trial_sigma,group)%>%
      summarize(n=n(),rms_error = mean(rms_error), abs_error = mean(abs_error))

#Error per block of 100 trials
ggboxplot(error, x = "tr_100", y = "rms_error", color = "trial_sigma", add= "jitter",legend = "right", ylab="Root mean square error", xlab = "Blocks" ) + facet_grid(~group) + scale_color_manual(values=c("darkorange", "darkslategrey"))
ggboxplot(error, x = "tr_100", y = "abs_error", color = "trial_sigma", add= "jitter" ,legend = "right", ylab="Absolute error", xlab = "Blocks" )+ facet_grid(~group)+ scale_color_manual(values=c("darkorange", "darkslategrey"))
```

##One-way repeated-measures ANOVA: DV = abs_error;  IV within = variability
##One-way repeated-measures ANOVA: DV = rms_error;  IV within = variability
```{r}
abs_error_anova<- df %>% mutate(abs_error = abs(distance_prior_response)) %>% aov(abs_error ~trial_sigma + group + trial_sigma  * group + Error(id/(trial_sigma)), data = .)
summary(abs_error_anova)
rms_error_anova<-aov(rms_error ~trial_sigma + group + trial_sigma * group + Error(id/(trial_sigma)), data=error)
summary(rms_error_anova)
```

##Responses over presented directions per group for different trial_sigma's
```{r}
#In the first three stable blocks
df%>%
  filter(tr_100 == "3" | tr_100 == "2"| tr_100 == "1")%>%
  group_by(id,distance_prior_conv,trial_sigma, group) %>%
  summarise(distance_prior_response_conv=mean(distance_prior_response_conv)) %>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=trial_sigma))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm',color='black') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(~group) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=trial_sigma), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = trial_sigma))  + scale_color_manual(values=c("tomato4", "darkgreen"))

#In second and third block (stable blocks without first one)
df%>%
  filter(tr_100 == "3" | tr_100 == "2")%>%
  group_by(id,distance_prior_conv,trial_sigma, group) %>%
  summarise(distance_prior_response_conv=mean(distance_prior_response_conv)) %>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=trial_sigma))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm',color='black') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(~group) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=trial_sigma), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = trial_sigma))  + scale_color_manual(values=c("tomato4", "darkgreen"))

#After shift in prior mean
df%>%
  filter(tr_100 == "4")%>%
  group_by(id,distance_prior_conv,trial_sigma, group) %>%
  summarise(distance_prior_response_conv=mean(distance_prior_response_conv)) %>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=trial_sigma))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm',color='black') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(~group) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=trial_sigma), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = trial_sigma))  + scale_color_manual(values=c("tomato4", "darkgreen"))



```


##Estimate slopes, intercepts and correlation coefficients with linear regression fits
```{r}

#Visualize data by plotting a linear regression for each individual
df%>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv)) + facet_grid(prior~trial_sigma) + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) +  labs(x = "motion directions distance relative to prior mean (°)", y = "mean estimates distance relative to the prior mean (°)")+  ggtitle("all participants") + theme_classic() + geom_smooth(aes(group=id),method = 'lm', color = 'gray80')+ geom_smooth(aes(distance_prior_conv,distance_prior_response_conv,color=group), method='lm' )


#Function to do a linear regression for each person's data and give the slope, intercept and correlation
est_slope<- function(x) {
  print(unique(x$id))
  my.lm <- lm(distance_prior_response_conv ~ distance_prior_conv, data = x )
  slope <- coef(my.lm)[2] 
  intercept <- coef(my.lm)["(Intercept)"]
  correlation <- cor(x$distance_prior_response_conv,x$distance_prior_conv)
  return(data.frame(s = unique(x$id),slope = slope,intercept = intercept, correlation = correlation))    
}


#Slope per person, group, trial_sigma and prior
df_est_cor_slope <- df %>% 
  group_by(id,group,session,trial_sigma,prior) %>% do(est_slope(.)) 

#scale these variables for lmer
df_est_cor_slope<- df_est_cor_slope %>% 
  group_by(id)%>%
  mutate(slope_z = scale(slope), 
         correlation_z = scale(correlation),
         intercept_z = scale(intercept))

#Summary table of slopes, intercepts and correlations
df_est_cor_slope %>% 
  group_by(id,group,trial_sigma,prior)%>%
  summarize(slope = mean(slope),intercept = mean(intercept), correlation = mean(correlation))%>%
  group_by(group,prior,trial_sigma)%>%
  summarize(slope = mean(slope),intercept = mean(intercept), correlation = mean(correlation))

#slopes in stable phase (prior 1) per group and per trial_sigma
df_est_cor_slope %>% filter(prior == 'prior 1')%>%ggboxplot(., x = "trial_sigma", y = "slope", add= "jitter",color = "group",legend = "right", ylab="slope", xlab = "Variability" )  + scale_color_manual(values=c("darkorange", "darkslategrey"))

#slopes after shift in prior mean per group and per trial_sigma
df_est_cor_slope %>% filter(prior == 'prior 2')%>%ggboxplot(., x = "trial_sigma", y = "slope", add= "jitter",color = "group",legend = "right", ylab="slope", xlab = "Variability" )  + scale_color_manual(values=c("darkorange", "darkslategrey"))

#intercepts in stable phase
df_est_cor_slope %>% filter(prior == 'prior 1')%>%ggboxplot(., x = "trial_sigma", y = "intercept", add= "jitter",color = "group",legend = "right", ylab="intercept", xlab = "Variability" )  + scale_color_manual(values=c("darkorange", "darkslategrey"))

#intercepts after shift in prior mean   
df_est_cor_slope %>% filter(prior == 'prior 2')%>%ggboxplot(., x = "trial_sigma", y = "intercept", add= "jitter",color = "group",legend = "right", ylab="intercept", xlab = "Variability" )  + scale_color_manual(values=c("darkorange", "darkslategrey"))

#Significant interaction between prior and group         
lmer_slope <- lmer(slope_z ~ group  * trial_sigma* prior + (trial_sigma|id)+ (prior|id), REML=F, data = df_est_cor_slope)
summary(lmer_slope)

lmer_intercept <- lmer(intercept_z ~ group * prior * trial_sigma+ (prior|id) + (trial_sigma|id), REML=F, data = df_est_cor_slope)
summary(lmer_intercept)

#slope for both groups for both priors
ggplot(df_est_cor_slope,aes(prior,slope,color=group)) + stat_summary(fun.y=base::mean, geom="line",aes(group=group)) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~trial_sigma)+ theme_classic() + scale_color_manual(values=c("darkorange", "darkslategrey"))

#intercepts for both groups for both priors
ggplot(df_est_cor_slope,aes(prior,intercept,color=group)) + stat_summary(fun.y=base::mean, geom="line",aes(group=group)) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~trial_sigma)+ theme_classic() + scale_color_manual(values=c("darkorange", "darkslategrey"))

#correlation for both groups for both priors
ggplot(df_est_cor_slope,aes(prior,correlation,color=group)) +  stat_summary(fun.y=base::mean, geom="line",aes(group=group)) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~trial_sigma)+ theme_classic() + scale_color_manual(values=c("darkorange", "darkslategrey"))

 
```


```{r}
#Direction estimates in noisy condition per group for stable phase
df%>%
  filter(tr_100 == "1"|tr_100 == "2"|tr_100 == "3")%>%filter(trial_sigma == "40")%>%
  group_by(id,prior,distance_prior_conv,trial_sigma,group)%>%
  summarise(distance_prior_response_conv = mean(distance_prior_response_conv))%>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=group))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(~trial_sigma) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=group), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = group))+ geom_point(color="gray80", size =0.5)  + scale_color_manual(values=c("darkorange", "darkslategrey"))

#Direction estimates in noisy condition for each block of 100 trials
df%>%
  filter(tr_100 == "1")%>%filter(trial_sigma == "40")%>%
  group_by(id,prior,distance_prior_conv,trial_sigma,group)%>%
  summarise(distance_prior_response_conv = mean(distance_prior_response_conv))%>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=group))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(prior~trial_sigma) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=group), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = group))+ geom_point(color="gray80", size =0.5)  + scale_color_manual(values=c("darkorange", "darkslategrey"))

df%>%
  filter(tr_100 == "2")%>%filter(trial_sigma == "40")%>%
  group_by(id,prior,distance_prior_conv,trial_sigma,group)%>%
  summarise(distance_prior_response_conv = mean(distance_prior_response_conv))%>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=group))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(prior~trial_sigma) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=group), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = group))+ geom_point(color="gray80", size =0.5)  + scale_color_manual(values=c("darkorange", "darkslategrey"))

df%>%
  filter(tr_100 == "3")%>%filter(trial_sigma == "40")%>%
  group_by(id,prior,distance_prior_conv,trial_sigma,group)%>%
  summarise(distance_prior_response_conv = mean(distance_prior_response_conv))%>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=group))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(prior~trial_sigma) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=group), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = group))+ geom_point(color="gray80", size =0.5)  + scale_color_manual(values=c("darkorange", "darkslategrey"))

df%>%
  filter(tr_100 == "4")%>%filter(trial_sigma == "40")%>%
  group_by(id,prior,distance_prior_conv,trial_sigma,group)%>%
  summarise(distance_prior_response_conv = mean(distance_prior_response_conv))%>%
  ggplot(aes(distance_prior_conv,distance_prior_response_conv ,color=group))+ geom_smooth(aes(distance_prior_conv,distance_prior_conv), method='lm') + geom_vline(xintercept=0, color='red') + geom_hline(yintercept=0, color='blue')+ facet_grid(prior~trial_sigma) + scale_y_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + scale_x_continuous(breaks = seq(-50,50, by=5), limits=c(-50,50)) + stat_summary(fun.y=base::mean, geom="point",aes(group=group), size=2) + theme_classic() + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2)+ stat_summary(fun.y = base::mean, geom="line", width = 0.2, aes(group = group))+ geom_point(color="gray80", size =0.5)  + scale_color_manual(values=c("darkorange", "darkslategrey"))

```

```{r}
#Slope per person, group, trial_sigma and tr_100
df_est_cor_slope <- df %>% 
  group_by(id,group,session,trial_sigma,tr_100) %>% do(est_slope(.)) 

#Scale variables
df_est_cor_slope<- df_est_cor_slope %>% 
  group_by(id)%>%
  mutate(slope_z = scale(slope), 
         correlation_z = scale(correlation),
         intercept_z = scale(intercept))

df_est_cor_slope %>% 
  group_by(id,group,trial_sigma,tr_100)%>%
  summarize(slope = mean(slope),intercept = mean(intercept), correlation = mean(correlation))%>%
  group_by(group,tr_100,trial_sigma)%>%
  summarize(slope = mean(slope),intercept = mean(intercept), correlation = mean(correlation))

#Slope per 100 trials
ggplot(df_est_cor_slope,aes(tr_100,slope,color=trial_sigma)) + stat_summary(fun.y=base::mean, geom="line",aes(group=trial_sigma)) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~group)+ theme_classic() + scale_color_manual(values=c("tomato4", "darkgreen"))

#Intercept per 100 trials
ggplot(df_est_cor_slope,aes(tr_100,intercept,color=trial_sigma)) + stat_summary(fun.y=base::mean, geom="line",aes(group=trial_sigma)) + geom_hline(yintercept=0, color='black') + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~group)+ theme_classic() + scale_color_manual(values=c("tomato4", "darkgreen"))

#Compare slopes between groups per 100 trials for noisy condition
df_est_cor_slope%>% filter(trial_sigma == '40') %>% ggplot(.,aes(tr_100,intercept,color=group)) + stat_summary(fun.y=base::mean, geom="line",aes(group=group)) + geom_hline(yintercept=0, color='black') + stat_summary(fun.data = "mean_cl_normal", geom="errorbar", width = 0.2) + theme_classic() + scale_color_manual(values=c("tomato4", "darkgreen"))

#Correlation per 100 trials
ggplot(df_est_cor_slope,aes(tr_100,correlation,color=group)) +  stat_summary(fun.y=base::mean, geom="line",aes(group=group)) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~trial_sigma)+ theme_classic() + scale_color_manual(values=c("darkorange", "darkslategrey"))


```

```{r}
#instantaneous slope per 50 trials
df_arc_slope<- df%>%group_by(block_index,id, group,trial_sigma)

ggplot(df_arc_slope,aes(block_index,arc_slope,color=group)) + stat_summary(fun.y=base::mean, geom="line",aes(group=group)) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~trial_sigma)+ theme_classic() + scale_color_manual(values=c("darkorange", "darkslategrey"))

lmer_slope <- lmer(arc_slope ~ group  * trial_sigma * block_index + (trial_sigma|id) + (block_index|id), REML=F, data = df)
summary(lmer_slope)

#Instantaneous slope of last 20 trials before and 20 trials after shift in prior
slopes_shift<-df%>%
  filter(distance_prior > 0 |distance_prior < 0)%>% #if distance prior is 0, slope is 0 as well
  filter((trial_index>287 & trial_index<307) | (trial_index<327 & trial_index>306))%>%
  group_by(id,group,block_index, trial_sigma)%>%
  summarise(arc_slope = mean(arc_slope))%>%
  spread(block_index,arc_slope)%>%
  rename(last_20 = '5', first_20 = '6')%>%
  mutate(difference_slope = first_20 -last_20)

slopes_shift_long<-df%>%
  filter(distance_prior > 0 |distance_prior < 0)%>%
  filter((trial_index>286 & trial_index<307) | (trial_index<328 & trial_index>306))%>%
  group_by(id,group,block_index, trial_sigma)%>%
  summarise(arc_slope = mean(arc_slope), n = n())

ggplot(slopes_shift_long,aes(block_index,arc_slope, color=group)) + geom_point(size=0.5, colour = "gray80") + geom_line(aes(group=id), colour = "gray80")+ stat_summary(fun.y=base::mean, geom="line",aes(group=group)) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(trial_sigma~group)+ theme_classic() + scale_color_manual(values=c("darkorange", "darkslategrey"))

aov_slope <- aov(arc_slope ~ trial_sigma*group*block_index + Error(id/(trial_sigma*block_index)), data = slopes_shift_long)
summary(aov_slope)

ggplot(slopes_shift_long,aes(block_index,arc_slope, color=group)) + stat_summary(fun.y=base::mean, geom="line",aes(group=group))+ geom_point(size=0.5) + stat_summary(fun.data = "mean_se", geom="errorbar", width = 0.2) + facet_grid(~trial_sigma)+ theme_classic() + scale_color_manual(values=c("darkorange", "darkslategrey"))

slopes_shift%>%
  ggboxplot(x = "trial_sigma", y = "difference_slope", color = "group", add= "jitter", legend = "right", ylab="difference_slope", xlab = "Trial_sigma" ) + scale_color_manual(values=c("darkorange", "darkslategrey"))

aov_slope <- aov(difference_slope ~ trial_sigma*group + Error(id/(trial_sigma)), data = slopes_shift)
summary(aov_slope)

```

#Distribution of estimates (like in Laquitaine and Gardner)
```{r}
ggplot(df,aes(distance_prior_response_conv)) + geom_histogram(binwidth=5) + geom_vline(xintercept=0, color = "red")+ facet_grid(distance_prior_conv~prior)

```
```


